### 2017-10-14 Gruba/10-appendix.tex

\stab(1) Most users of group one are male (as shown in Sub-Fig. \ref{fig:subfig1:fig11}), and Sub-Fig. \ref{fig:subfig1:fig12} shows that they are mainly in Beijing(北京). Most of them have number of followees similar as followers (as shown in Sub-Fig. \ref{fig:subfig1:fig14}). The most active time of this group is mainly between 10 am and 12 am (as shown in Sub-Fig. \ref{fig:subfig1:fig15} and \ref{fig:subfig1:fig16}).

\stab(2) The users of group two are mostly female (as shown in Sub-Fig. \ref{fig:subfig2:fig21}) and are also mainly in Beijing (北京) (shown as Sub-Fig. \ref{fig:subfig2:fig22}). Similar as group one, most of them have followees close to followers (as shown in Sub-Fig. \ref{fig:subfig2:fig24}). The most active time of this group is mainly between 10 pm and 12 pm (as shown in Sub-Fig. \ref{fig:subfig2:fig25} and \ref{fig:subfig2:fig26}).

@@

\stab(4) Most users of group four are female (as shown in Sub-Fig. \ref{fig:subfig4:fig41}), and they come from a wide range of provinces just as group three (as shown in Sub-Fig. \ref{fig:subfig4:fig42}). Most of these users have number of followers far more than followees (as shown in Sub-Fig. \ref{fig:subfig4:fig44}). And the most active time of these users is mainly between 10 pm and 12 pm (as shown in Sub-Fig. \ref{fig:subfig4:fig45} and \ref{fig:subfig4:fig46}).

According to Sub-Fig. \ref{fig:subfig1:fig13}, \ref{fig:subfig2:fig23}, \ref{fig:subfig3:fig33} and \ref{fig:subfig4:fig43},
the number distribution of microblogs for four groups is similar with each other.
We visualized each group's long-term interest expressed as words cloud (shown in Sub-Fig. \ref{fig:subfig1:fig19}, \ref{fig:subfig2:fig29}, \ref{fig:subfig3:fig39} and \ref{fig:subfig4:fig49}), as we can see, group one and group three have similar interest.

>>>>

\stab(1) Most users of group one are male (as shown in Sub-Fig. \ref{fig:subfig1:fig11}), and Sub-Fig. \ref{fig:subfig1:fig12} shows that they are mainly in Beijing(北京). The amount of their followees is mostly similar as their followers (as shown in Sub-Fig. \ref{fig:subfig1:fig14}). The most active time of this group is mainly between 10 am and 12 am (as shown in Sub-Fig. \ref{fig:subfig1:fig15} and \ref{fig:subfig1:fig16}).

\stab(2) Mostly users of group two are  female (as shown in Sub-Fig. \ref{fig:subfig2:fig21}) and are also mainly in Beijing (北京) (shown as Sub-Fig. \ref{fig:subfig2:fig22}). Similar to group one, most of them have followees close to followers (as shown in Sub-Fig. \ref{fig:subfig2:fig24}). The most active time of this group is mainly between 10 pm and 12 pm (as shown in Sub-Fig. \ref{fig:subfig2:fig25} and \ref{fig:subfig2:fig26}).

@@

\stab(4) Most users of group four are female (as shown in Sub-Fig. \ref{fig:subfig4:fig41}), and they come from a wide range of provinces just as group three (as shown in Sub-Fig. \ref{fig:subfig4:fig42}). Most of these users have the amount  of followers far more than followees (as shown in Sub-Fig. \ref{fig:subfig4:fig44}). And the most active time of these users is mainly between 10 pm and 12 pm (as shown in Sub-Fig. \ref{fig:subfig4:fig45} and \ref{fig:subfig4:fig46}).

According to Sub-Figs. \ref{fig:subfig1:fig13}, \ref{fig:subfig2:fig23}, \ref{fig:subfig3:fig33} and \ref{fig:subfig4:fig43},
the number distribution of microblogs for four groups is similar with each other.
We visualize each group's long-term interest expressed as words cloud (shown in Sub-Figs. \ref{fig:subfig1:fig19}, \ref{fig:subfig2:fig29}, \ref{fig:subfig3:fig39} and \ref{fig:subfig4:fig49}). As we can see, group one and group three have similar interests.
